Make any stupid plot you want

### 2020-12-18 draft/sections/math.tex
artists + pdf
moved mrks out

The localized section of fibers $\iota^*\tau: U \rightarrow \iota^*E$ is the sheaf $O(E)$ with germ $\xi^*\tau$. The neighborhood of points the sheaf lies over is the stalk $\mathscr{F}_k$ \cite{StalkSheaf2019,spanier1989algebraic}

@@

which through $\iota$ gets the data in $E$ at and near to $k$. Restricting the artist to the sheaf means the artist knows the data in $F$ and also has access to derivatives of the data. This property is useful for some visual transformations.

\subsection{Prerender Space}
\label{sec:display}

@@

To draw an image, a region, $H$ is inverse mapped into a region $s \in S$ where
\begin{equation}
s = \rho^{-1}_{XY}(xy)
\end{equation}
such that the rest of the fields in $\mathbb{R}^{7}$ are then integrated over $s$ to yield the remaining fields in $p$

\begin{align}
    R(p) &= \oint_s \rho_R(s)ds^{2}\\
    G(p) &= \oint_s \rho_G(s)ds^{2}\\
    B(p) &= \oint_s \rho_B(s)ds^{2}
\end{align}

@@

The artist is a mapping from the sheaf $O(E)$ representing the data to a pre-render space $O(H)$. 
\begin{equation}
    A: O(E) \rightarrow O(H)
\end{equation}

The artist acts on a sheaf because some visual characterstics, such as line thickness, need more information than just the data at a point. The artist through $F: E \rightarrow V$ maps from data space to visual variable  \cite{carpendaleVisualRepresentationSemiology,bertinIIPropertiesGraphic2011,munznerWhatDataAbstraction2014} space

\begin{equation}
    \begin{tikzcd}
        E \arrow[r, "\nu" description]                                & V \\
        K \arrow[u, "\tau" description] \arrow[ru, "\mu" description] &  
    \end{tikzcd}
\end{equation}

such that $\nu: \tau \mapsto \mu$ is a homorphism where $\tau$ and $\mu$ are equivariant such that the properties of the field type persist in the visual representation. The map $\xi: S \rightarrow K$ goes from a region $s$ to it associated $k$ 
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi" description]              & H \arrow[d, "\pi" description]                                    \\
        K \arrow[u, "\tau" description, bend right] & S \arrow[l, "\xi" description] \arrow[lu, "\xi^*\tau" description]
        \end{tikzcd}
\end{equation}
and can be pulled back up to $E$ (or $V$) such that for a region $s$ there is an associated record $\tau$ and visual mapping $\mu$. The visual fiber bundle $V$ gets pulled back over $S$ via $\xi$ such that 
\begin{equation}

\end{equation}
the composition $q \circ \xi^*\mu$ generates the $\rho$ function described in section~\ref{sec:display}.

\subsubsection{Channels}
Each $\nu$ function maps a field $\tau_c$ to a paramterized visual field $\mu$, for example the color or shape visual channels \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}. The set of $\nus$ is a functor from data to visual space such that any $\nu$ is an equivariant map if

@@

%nu is functor
% examples of nu \tau\mu pairs - ordinal
%maybe param is the wrong thing 
Define a channel in terms of nus
This is what we mean by equivariance: 
step thrpoughh measurment scale groups
doesn't matter where computation lives

@@

>>>>

The localized section of fibers $\iota^*\tau: U \rightarrow \iota^*E$ is the sheaf $O(E)$ with germ of $\xi^*\tau$. The neighborhood of points the sheaf lies over is the stalk $\mathscr{F}_k$ \cite{StalkSheaf2019,spanier1989algebraic}

@@

which through $\iota$ gets the data in $E$ at and near to $k$. Restricting the artist to the sheaf means the artist knows the data in $F$ and also has access to derivatives of the data. This property is useful for some visual transformations. 
%% gives all direvatives but we need the jet which is Add stuff about jets
\subsection{Prerender Space}
\label{sec:display}

@@

To draw an image, a region, $H$ is inverse mapped into a region $s \in S$ where
\begin{equation}
s = \rho^{-1}_{XY}(xy)
\end{equation}
such that the rest of the fields in $\mathbb{R}^{7}$ are then integrated over $s$ to yield the remaining fields in $p$
%%change the integral to a double integral
\begin{align}
    R(p) &= \iint_s \rho_R(s)ds^{2}\\
    G(p) &= \iint_s \rho_G(s)ds^{2}\\
    B(p) &= \iint_s \rho_B(s)ds^{2}
\end{align}

@@

The artist is a mapping from the sheaf $O(E)$ representing the data to a pre-render space $O(H)$. 
\begin{equation}
    A: O(E) \rightarrow O(H)
\end{equation}
The artist is composed of two stages, data $E$ to visual mappings $V$ and $V$ mappings composited to a visual in prerender space $H$:
\begin{equation}
insert triangle here
\end{equation}

The first stage of the artist $F: E \rightarrow V$ maps from data space to visual variable  \cite{carpendaleVisualRepresentationSemiology,bertinIIPropertiesGraphic2011,munznerWhatDataAbstraction2014} space
%%include the $
\begin{equation}
    \begin{tikzcd}
        E \arrow[r, "\nu" description]                                & V \\
        K \arrow[u, "\tau" description] \arrow[ru, "\mu" description] &  
    \end{tikzcd}
\end{equation}

such that $\nu: \tau \mapsto \mu$ is a homorphism where $\tau$ and $\mu$ are equivariant such that the properties of the field type persist in the visual representation. The map $\xi: S \rightarrow K$ goes from a region $s$ to it associated $k$ %%remove the taus from the diagram
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi" description]              & H \arrow[d, "\pi" description]                                    \\
        K \arrow[u, "\tau" description, bend right] & S \arrow[l, "\xi" description] \arrow[lu, "\xi^*\tau" description]
        \end{tikzcd}
\end{equation}
such that when $\xi(s) = k$, there is a mapping from screen space to k  $\xi^*\tau(s) = \tau(k)$. The visual fiber bundle $V$ gets pulled back over $S$ via $\xi$ such that 
\begin{equation}
    \begin{tikzcd}
        \xi^*V \arrow[r, "q"']                      & H \\
        S \arrow[u, "\xi^*\mu"] \arrow[ru, "\rho"'] &  
        \end{tikzcd}
\end{equation}
the composition $q \circ \xi^*\mu$ generates the $\rho$ function described in section~\ref{sec:display}.

\subsubsection{Channels}
Each $\nu$ function maps a field $\tau_c$ to a paramterized visual field $\mu$, for example the color or shape visual channels \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}. The set of $\nu$ is a functor from data to visual space such that any $\nu$ is an equivariant map if

@@

$E$ or $J(E)$
%nu is functor
% examples of nu \tau\mu pairs - ordinal
%maybe param is the wrong thing 
Define a channel in terms of nus
This is what we mean by equivariance: 
step thrpoughh measurment scale groups
doesn't matter where computation lives

@@

%For example, given a categorical field $c$ carry through temperature, maybe picture?
